---
title: "Games Code"
author: "Rafael Guimaraes, Yilang Tang and Yuanxi Yao"
date: "3/28/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
df.train <- read.csv("~/Desktop/Brandes/Analysing Big Data 2/Analysing Big Data 2/data/Betting.csv")
df.test <- read.csv("~/Desktop/Brandes/Analysing Big Data 2/Analysing Big Data 2/data/BettingTest.csv", header=T)

```

### Question 1

Write down the equation to predict thw chnce of winning.

```{r cars}
library(nnet)
df.train$prog2<-relevel(df.train$Match_O, ref="Loss")
train<-multinom(prog2~HTGD+RED.H+RED.A+POINTS_H+POINTS_A+TOTAL_H_P+TOTAL_A_P+FGS.0+FGS.1, 
               data=df.train)

```

```{r echo=FALSE}
summary(train)
```


### Question 2:  
According to your model, how do red cards conceded by the Home and Away team influence the outcome of a match. Your response should not be numeric, but qualitative. Based on your understanding of the sport, speculate about possible reasons for these findings.

### Question 3:  
Under what circumstances is it informative to include points scored by a team in the prior season to predict the outcome of a match?



