---
title: "New White wine"
author: "Rafael Guimaraes, Yilang Tang and Yuanxi Yao"
date: "4/4/2017"
output: html_document
---

```{r packages}
library(fBasics) # Show basic aspect of the data
library(readr)  # provide additional data-reading functions
library(corrplot) # attractive correlation graphs
library(ggplot2) # for plots
library(data.table)
library(dplyr)
library(reshape2)
library(corrgram)
library(MASS)  # Package MASS includes the LDA function
library(ggplot2)
library(lattice)
library(e1071)  # for SVM model
library(nnet)   # for basic neural net
library(party)
library(car)
```
#  ---------------------------------------------------------------------------
#  Preparing data
#  ---------------------------------------------------------------------------




# Loading data
```{r loading}



white_wine <- read.csv("~/Desktop/Brandes/Analysing Big Data 2/Analysing Big Data 2/data/winequality-white.csv")


new_white <- read.csv("~/Desktop/Brandes/Analysing Big Data 2/Analysing Big Data 2/data/new_white.csv")



View(white_wine)
dim(white_wine)
head(white_wine)
names(white_wine)
summary(white_wine)
str(white_wine)
```

#  ---------------------------------------------------------------------------
#  Quality as a factor
#  ---------------------------------------------------------------------------
```{r qualityfactor}
white_wine$quality <- as.factor(white_wine$quality)
```

#  ---------------------------------------------------------------------------
#  Creating a traing set
#  ---------------------------------------------------------------------------
```{r training set}
set.seed(1980)   # initialize the randomm number generator


temp <- sample(2,nrow(white_wine),replace=TRUE, prob=c(0.80,0.20)) # vector of random 1s & 2s

train <- white_wine[temp==1,]  # training subset uses rows where temp = 1
test <- white_wine[temp==2,]

dim(train)
dim(test)
View(head(train))
head(test)
names(train)
```
#  ---------------------------------------------------------------------------
#  Create a formula
#  ---------------------------------------------------------------------------

We choose 5 variables that are strongest correlated to the quality, they are alcohol(0.42),density(-0.30), volatile acidity(-0.22), chlorides(-0.21) and total sulfur dioxide(-0.15)
```{r formula}
form <- as.formula("quality~volatile.acidity+chlorides+total.sulfur.dioxide+density+alcohol")
```
#  ---------------------------------------------------------------------------
#  Model1:Multinomial regression
#  ---------------------------------------------------------------------------
1.Multinomial regression
```{r multinomial regression}
mod <- multinom(form, data=train)
summary(mod$fitted.values)
lgpred <- predict(mod,test)
table(lgpred)
```
2.Confusion Matrix
```{r matrix1}
tab <- table(lgpred, test$quality)
print(tab)
```
3.misclassification rate
```{r misrate1}
1-sum(diag(tab))/sum(tab)  
```
#  ---------------------------------------------------------------------------
#  Model2:CART model
#  ---------------------------------------------------------------------------
1.CART Model
```{r CART}
tree <- ctree(form, train, 
              controls=ctree_control(mincriterion=0.90, minsplit=10))
pred_tree <- predict(tree, train)
table(pred_tree)
```
2.Confusion Matrix
```{r matrix2}
tab <- table(pred_tree, train$quality)
print(tab)
```
3.misclassification rate
```{r misrate2}
1-sum(diag(tab))/sum(tab)
```
#  ---------------------------------------------------------------------------
#  Model3:Linear Discriminant Analysis
#  ---------------------------------------------------------------------------
1.LDA
```{r LDA}
fit <- lda(form, data=train,
           na.action="na.omit") 
pred_lda <- predict(fit, train)$class  
table(pred_lda) 
```
2.Confusion Matrix
```{r Matrix3}
tab <- table(pred_lda, train$quality)
print(tab)
```
3.misclassification rate
```{r misrate3}
1-sum(diag(tab))/sum(tab) 
```
#  ---------------------------------------------------------------------------
#  Model4:SVM - Support Vector Machine
#  ---------------------------------------------------------------------------
1.SVM
```{r SVM}
svm1 <- svm(form, data=train)
summary(svm1)
pred_svm <- fitted(svm1)
table(pred_svm)
```
2.Confusion Matrix
```{r Matrix4}
tab <- table(pred_svm, train$quality)
print(tab)
```
3.misclassification rate
```{r misrate4}
1-sum(diag(tab))/sum(tab)  
```
#  ---------------------------------------------------------------------------
#  Model5: Neural Net
#  ---------------------------------------------------------------------------
1.Neural Net
```{r NN}
mod_nn <- nnet(form, data = train, size = 2)
pred_nn <- predict(mod_nn, data=train, type = "class")  
table(pred_nn)
```
2.Confusion Matrix
```{r Matrix5}
tab <- table(pred_nn, train$quality)
print(tab)
```
3.misclassification rate
```{r misrate5}
1-sum(diag(tab))/sum(tab)
```
-----------------------------------------------------------------------------------
#Prediction for the 10 new wine
SVM offers the lowest misclassification rate at 45.22%, now we use this methods to predict for the new wine.
```{r new wine}
pred <- predict(svm1,new_white)
